\documentclass[line,margin]{res}
	\usepackage{fancyhdr}
	\pagestyle{fancy}
	\renewcommand{\headrulewidth}{0pt}
	\usepackage[usenames,dvipsnames]{xcolor}
	\usepackage[colorlinks=true,linkcolor=blue,urlcolor=NavyBlue,citecolor=Fuchsia]{hyperref}
	\usepackage[T1]{fontenc}
	\usepackage[default]{sourcesanspro}

	\newsectionwidth{0pt}
	\setlength{\headsep}{12pt}
	\setlength{\textheight}{9.5in}
	\topmargin=-0.5in

	\lfoot {} \cfoot {}
	\rfoot {\scriptsize{Resume viewable online at \href{https://github.com/rkblake/Resume/blob/master/randallblake_resume.pdf}{https://github.com/rkblake/Resume/blob/master/randallblake\_resume.pdf}}}


\begin{document}
	\name{Randall Blake}
	\address{(512)574-6609 ||
	\href{https://www.linkedin.com/in/randallblake/}{linkedin.com/in/randallblake} ||
	\href{mailto:blakerandall0@gmail.com}{blakerandall0@gmail.com}}

\begin{resume}

\vspace{8pt}
%\section{Summary}
%\vspace{22pt}
%	\begin{itemize} \itemsep -2pt
%	\item Interested in pursuing a career in AI or computer graphics
%	\item Experience with version control systems, continuous integration, and bug tracking
%	\item Studying AI, computational neural networks, and computer graphics
%	\end{itemize}

\vspace{-4pt}


\vspace{-4pt}
\section{Experience}
\vspace{12pt}

Full Stack Engineer at Fencing Star
\hfill Jan. 2021 - Present
\begin{itemize} \itemsep -2pt
	\item Built a full-stack app that tracks user’s progress using Docker, Python/Flask, and PostgreSQL.
	\item Deployed and maintained code on DigitalOcean’s cloud server running Linux.
	\item Integrated Stripe’s API to manage customer payments and SendGrid to send invoices.
%	\item (\href{https://fencingstar.rkblake.com}{\texttt{fencingstar.rkblake.com}}).
	\item Created \href{https://fencingstar.rkblake.com}{\texttt{fencingstar.rkblake.com}}, which received positive feedback from users.
\end{itemize}
\vspace{-6pt}
Software Engineer at IXIA/Keysight
\hfill Mar. 2018 - Aug. 2020
	\begin{itemize} \itemsep -2pt
	\item Developed C applications to extract data from network traffic at 100Gib/S and parsed TCP/UDP packets and other Layer 7 protocols.
	\item Utilized Robot and traffic generators to write QA and regression tests for debugging network protocols.
	\item Set up Docker/Kubernetes environment to run product on virtual switches and earned the team their first \$1M quarter by providing new features for customers.
%	\item Set up Docker/Kubernetes environment to run product on virtual switches.
%	\item Earned the team their first \$1M quarter by providing new features for customers.
	\end{itemize}
\vspace{-6pt}
Software Engineering internship at Apcon
\hfill  Jan. 2016 - Sep. 2017
\begin{itemize} \itemsep -2pt
	\item Conducted static code analysis and regression testing to find and fix bugs.
	\item Migrated software to the cloud and optimized Linux installation by reducing package size.
	\item Expanded server back-end and front-end using Adobe Flex and C++.

	\end{itemize}

\vspace{-4pt}
\section{Education}
\vspace{12pt}
University of Texas at Dallas \hfill 2013-2017 \\
\vspace{-12pt}
\begin{itemize} \itemsep -2pt
	\item Bachelor's of Science in Computer Science 2017
\end{itemize}

\vspace{-4pt}
\section{Projects}
\vspace{12pt}

%\vspace{6pt}
%Open Source C++ OpenGL/SDL Game and Physics Engine
%\hfill 2015
%	\begin{itemize} \itemsep -2pt
%	\item Personal project using OpenGL 3.3, SDL2, and Lua
%	\item Working graphical renderer and physics simulator
%	\item (\href{https://github.com/justaddbass/ExclusionEngine}{\texttt{github.com/justaddbass/ExclusionEngine}})
%	\end{itemize}

Fencing Tournament Organizer Web Service
\hfill 2017-2019
	\begin{itemize} \itemsep -2pt
		\item Built a website in Python/Flask and SQLite3 for organizers to run tournaments offline or online.
		\item Developed a database to store results, allowing competitors to view live scores and brackets.
		\item Used by the Southwest Intercollegiate Fencing Association for local tournaments.
%		\item (\href{https://github.com/rkblake/FencingTournamentTool}{\texttt{github.com/rkblake/FencingTournamentTool}}).
	\end{itemize}

\vspace{-6pt}
Flat-Panel Airborne Radio Control
\hfill 2017
	\begin{itemize} \itemsep -2pt
		\item Completed semester-long senior design project in a team of 6 with academic advisor.
		\item Worked with Sponsor, Rockwell Collins, to develop software for radio control and maintenance.
		\item Created an interface to automate testing of on-board radios and report outcome.
	\end{itemize}

\vspace{-6pt}
Solar System Simulator
\hfill 2017
	\begin{itemize} \itemsep -2pt
		\item Simulated orbital mechanics of planets around a star using Newtonian physics.
		\item Utilized OpenGL and SDL2 to display graphics that the user can navigate around in.
		\item (\href{https://github.com/rkblake/SolarSim/}{\texttt{github.com/rkblake/SolarSim/}}).
	\end{itemize}

%\vspace{-8pt}
%Lua C++ Interface
%\hfill 2017
%	\begin{itemize} \itemsep -2pt
%		\item Reads variables from Lua script into C++
%		\item Useful for easy configuration files and hot swapping code
%		\item  (\href{https://github.com/justaddbass/LuaConf}{\texttt{github.com/justaddbass/LuaConf}})
%		\end{itemize}

%\vspace{6pt}
%Python iTunes Library generator
%\hfill 2014
%	\begin{itemize} \itemsep -2pt
%	\item Uses mutagen and ElementTree to read id3 tags and write to xml
%	\item (\href{https://github.com/justaddbass/iTunesLibGen}{\texttt{github.com/justaddbass/iTunesLibGen}})
%	\end{itemize}

%\vspace{-8pt}
%ECS Maze Solving Toy Car
%\hfill 2014
%	\begin{itemize} \itemsep -2pt
%	\item Freshman Engineering semester project, team of 5
%	\item Uses Raspberry Pi, ultrasonic sensors and a Python script to navigate a maze
%	\end{itemize}

\vspace{-6pt}
Real-Time Strategy AI Competition
\hfill 2010-2012
\begin{itemize} \itemsep -2pt
	\item Worked in a 2-person team on a Real-Time Strategy AI in C++ that played against other AI.
	\item Created an AI that managed resources and up to 200 units to defeat an opponent.
	\item Dortmund University of Technology’s Computational Intelligence and Games (CIG) 2011 Starcraft AI
	competitor (\href{http://ls11-www.cs.tu-dortmund.de/rts-competition/starcraft-cig2011}{\texttt{ls11-www.cs.tu-dortmund.de/rts-competition/starcraft-cig2011}}).
\end{itemize}

\vspace{-4pt}
\section{Skills}
\vspace{22pt}
	\begin{itemize} \itemsep -2pt
		\item Programming Languages: C/C++, Python, Javascript, HTML, Erlang, Lua, .NET, Java \ldots
		\item Frameworks: Flask, OpenGL, SDL2, Node.js, Vue.js, PostgreSQL, MongoDB \ldots
		\item Technical Skills: git, SVN, GDB, REST, Jenkins, Docker, Kubernetes, Linux, AWS, Jira, Agile \ldots
	\end{itemize}

\vspace{-4pt}
\section{Miscellaneous}
\vspace{22pt}
	\begin{itemize} \itemsep -2pt
	\item Former captain of college fencing club who coached and lead teams to victories at state competitions.
	\item Participated in multiple Game Jams programming games in 48-hours.
	\item Competed in Cyber security competitions with UTD's Computer Security Group.
	\item Ask me (\href{https://github.com/rkblake}{\texttt{github.com/rkblake}}) about my other projects!
	\end{itemize}

\end{resume}
\end{document}
